Here are all the packages used for this project:
```{r}
library(RCurl)
library(tidyverse)
library(ggplot2)
library(hrbrthemes)
library(ggcorrplot)
library(fmsb)
```


## Downloading all the csv files from the online github repo

The naming convention for each file goes as follows:

dataset012 using camelCase

0: state or county
1: data measured
2: demographic if listed

```{r}
#Reads in all the datasets

#Reading in county vaccinations
datasetCountyVaccAge <- read.csv("https://raw.githubusercontent.com/zch5/INFSCI0310-FinalProject/main/Datasets/County%20Vaccinations/COVID-19_Vaccinations_by_Age_Group_Current_County_Health.csv")
datasetCountyVaccResidence <- read.csv("https://raw.githubusercontent.com/zch5/INFSCI0310-FinalProject/main/Datasets/County%20Vaccinations/COVID-19_Vaccinations_by_Day_by_County_of_Residence_Current_Health.csv")
datasetCountyVaccEthnicity <- read.csv("https://raw.githubusercontent.com/zch5/INFSCI0310-FinalProject/main/Datasets/County%20Vaccinations/COVID-19_Vaccinations_by_Ethnicity_Current_County_Health.csv")
datasetCountyVaccGender <- read.csv("https://raw.githubusercontent.com/zch5/INFSCI0310-FinalProject/main/Datasets/County%20Vaccinations/COVID-19_Vaccinations_by_Gender_Current_County_Health.csv")
datasetCountyVaccRace <- read.csv("https://raw.githubusercontent.com/zch5/INFSCI0310-FinalProject/main/Datasets/County%20Vaccinations/COVID-19_Vaccinations_by_Race_Current_County_Health.csv")
datasetCountyVaccCurrresidence <- read.csv("https://raw.githubusercontent.com/zch5/INFSCI0310-FinalProject/main/Datasets/County%20Vaccinations/COVID-19_Vaccinations_by_Residence_Current_County_Health.csv")

#Reading in state vaccinations
datasetStateVaccAge <- read.csv("https://raw.githubusercontent.com/zch5/INFSCI0310-FinalProject/main/Datasets/PA%20Vaccinations/COVID-19_Vaccinations_by_Age_Group_Current_Statewide_Health.csv")
datasetStateVaccEthnicity <- read.csv("https://raw.githubusercontent.com/zch5/INFSCI0310-FinalProject/main/Datasets/PA%20Vaccinations/COVID-19_Vaccinations_by_Ethnicity_Current_Statewide_Health.csv")
datasetStateVaccGender <- read.csv("https://raw.githubusercontent.com/zch5/INFSCI0310-FinalProject/main/Datasets/PA%20Vaccinations/COVID-19_Vaccinations_by_Gender_Current_Statewide_Health.csv")
datasetStateVaccRace <- read.csv("https://raw.githubusercontent.com/zch5/INFSCI0310-FinalProject/main/Datasets/PA%20Vaccinations/COVID-19_Vaccinations_by_Race_Current_Statewide_Health.csv")

#Reading in other datasets
datasetCountyCases <- read.csv("https://raw.githubusercontent.com/zch5/INFSCI0310-FinalProject/main/Datasets/COVID-19_Aggregate_Cases_Current_Daily_County_Health.csv")
datasetCountyDeaths <- read.csv("https://raw.githubusercontent.com/zch5/INFSCI0310-FinalProject/main/Datasets/COVID-19_Aggregate_Death_Data_Current_Daily_County_Health.csv")
datasetCountyHospitalizations <- read.csv("https://raw.githubusercontent.com/zch5/INFSCI0310-FinalProject/main/Datasets/COVID-19_Aggregate_Hospitalizations_Current_Daily_County_Health.csv")
datasetStateTestcounts <- read.csv("https://raw.githubusercontent.com/zch5/INFSCI0310-FinalProject/main/Datasets/COVID-19_PCR_Test_Counts_March_2020_-_Current_Statewide_Health.csv")

#Others folder
datasetStateDemographics <- read.csv("https://raw.githubusercontent.com/zch5/INFSCI0310-FinalProject/main/Datasets/Others/Race%20and%20Ethnicity.csv")
```


```{r}
#Changes all not a numbers to 0s

datasetCountyVaccAge[is.na(datasetCountyVaccAge)] <- 0
datasetCountyVaccResidence[is.na(datasetCountyVaccResidence)] <- 0
datasetCountyVaccEthnicity[is.na(datasetCountyVaccEthnicity)] <- 0
datasetCountyVaccGender[is.na(datasetCountyVaccGender)] <- 0
datasetCountyVaccRace[is.na(datasetCountyVaccRace)] <- 0
datasetCountyVaccCurrresidence[is.na(datasetCountyVaccCurrresidence)] <- 0

datasetStateVaccAge[is.na(datasetStateVaccAge)] <- 0
datasetStateVaccEthnicity[is.na(datasetStateVaccEthnicity)] <- 0
datasetStateVaccGender[is.na(datasetStateVaccGender)] <- 0
datasetStateVaccRace[is.na(datasetStateVaccRace)] <- 0

datasetCountyCases[is.na(datasetCountyCases)] <- 0
datasetCountyDeaths[is.na(datasetCountyDeaths)] <- 0
datasetCountyHospitalizations[is.na(datasetCountyHospitalizations)] <- 0
datasetStateTestcounts[is.na(datasetStateTestcounts)] <- 0

```

```{r}
head(datasetCountyVaccAge)
```


```{r}

#Add code for graphs and such here
#lm(Airborn.Isolation.Beds.Available~Medical.Surgical.Beds.Available, data = datasetCountyHospitalizations)
#newframe = merge(datasetStateVaccRace, datasetStateDemographics, by="Race")
#head(newframe)
#ggplot(datasetStateVaccRace, aes(x=Partially.Covered, y=Fully.Covered, color=Race)) + geom_point(size=6) + theme_ipsum()
```




Lets look at vaccinations by gender
Note that partially covered DOES NOT include fully covered
```{r}

#df = subset(datasetCountyVaccAge, select = -c(County.Name))
#df$Partially.Covered.Age.Group.15.19 <- as.numeric((datasetCountyVaccAge$Partially.Covered.Age.Group.15.19))
head(datasetStateVaccGender)

options(scipen=5)          #Tells R not to do scientific notation
ggplot(datasetStateVaccGender, aes(Gender, Partially.Covered, fill=Gender)) + geom_bar(stat = "identity")
ggplot(datasetStateVaccGender, aes(Gender, Fully.Covered, fill=Gender)) + geom_bar(stat = "identity")
```


Lets look at vaccinations by age
Note that partially covered DOES NOT include fully covered
```{r}
df = datasetStateVaccAge
head(df)

#Sets up everything over 100
df[1, 1] = 'Over 100'
df[1, 2] = df[1, 2] + df[10, 2]
df[1, 3] = df[1, 3] + df[10, 3]
df <- df[-c(10),]

options(scipen=5)          #Tells R not to do scientific notation
graph1 <- ggplot(df, aes(Age.Group, Partially.Covered, fill=Age.Group)) + geom_bar(stat = "identity")
graph1 + theme(axis.text.x = element_text(angle = 60, hjust = 1))
graph2 <- ggplot(df, aes(Age.Group, Fully.Covered, fill=Age.Group)) + geom_bar(stat = "identity")
graph2 + theme(axis.text.x = element_text(angle = 60, hjust = 1))
```

Lets look at vaccinations by ethnicity
Note that partially covered DOES NOT include fully covered
```{r}
df = datasetStateVaccEthnicity
head(df)


options(scipen=5)          #Tells R not to do scientific notation
graph1 <- ggplot(df, aes(Ethnicity, Partially.Covered, fill=Ethnicity)) + geom_bar(stat = "identity")
graph1 + theme(axis.text.x = element_text(angle = 60, hjust = 1))
graph2 <- ggplot(df, aes(Ethnicity, Fully.Covered, fill=Ethnicity)) + geom_bar(stat = "identity")
graph2 + theme(axis.text.x = element_text(angle = 60, hjust = 1))
```

Lets look at vaccinations by race
Note that partially covered DOES NOT include fully covered
```{r}
df = datasetStateVaccRace
head(df)


options(scipen=5)          #Tells R not to do scientific notation
graph1 <- ggplot(df, aes(Race, Partially.Covered, fill=Race)) + geom_bar(stat = "identity")
graph1 + theme(axis.text.x = element_text(angle = 60, hjust = 1))
graph2 <- ggplot(df, aes(Race, Fully.Covered, fill=Race)) + geom_bar(stat = "identity")
graph2 + theme(axis.text.x = element_text(angle = 60, hjust = 1))

#Comparing that to state stats
df1 = datasetStateDemographics
df2 = data.frame("Race" = c("African American", "Asian", "Multiple/Other", "Native American", "Unknown", "White"), "Population" = 0)
df2[1, 2] = df1[3, 11]
df2[2, 2] = df1[7, 11]
df2[3, 2] = df1[13, 11]
df2[4, 2] = df1[5, 11]
df2[5, 2] = df1[11, 11]
df2[6, 2] = df1[1, 11]
df2
graph3 <- ggplot(df2, aes(Race, Population, fill=Race)) + geom_bar(stat = "identity")
graph3 + theme(axis.text.x = element_text(angle = 60, hjust = 1))
```
Lets look at vaccinations by County
```{r}
df <- datasetCountyVaccGender
df

#Splitting in half
df1 = df[1:204,]
df2 = df[205:407,]


x = df1$County.Name
y = df1$Total.Count

graph = ggplot(df1, aes(x=x, y=y)) + geom_point() + geom_segment(aes(x=x, xend=x, y=0, yend=y))
graph + theme(axis.text.x = element_text(angle = 60, hjust = 1)) + ggtitle("COVID-19 Vaccines by PA County (1)") + xlab("County") + ylab("Vaccination Total")

x = df2$County.Name
y = df2$Total.Count

graph = ggplot(df2, aes(x=x, y=y)) + geom_point() + geom_segment(aes(x=x, xend=x, y=0, yend=y))
graph + theme(axis.text.x = element_text(angle = 60, hjust = 1)) + ggtitle("COVID-19 Vaccines by PA County (2)") + xlab("County") + ylab("Vaccination Total")
```


